---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.height = 3,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spquery

<!-- badges: start -->
[![R-CMD-check](https://github.com/Nowosad/spquery/workflows/pkgdown/badge.svg)](https://github.com/Nowosad/spquery/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The **spquery** package performs several queries based on spatial raster data.

## Installation

You can install the development version of spquery from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Nowosad/spquery")
```

## Example

```{r}
library(terra)
library(sf)
library(spquery)
```

```{r}
ta = rast(system.file("raster/ta_scaled.tif", package = "spquery"))[[1:4]]
plot(ta, nr = 1)
```

```{r}
pr = rast(system.file("raster/pr_scaled.tif", package = "spquery"))[[1:4]]
plot(pr, nr = 1)
```

### Comparison

```{r, fig.height=5}
re = spq_compare(ta, pr, dist_fun = "jensen-shannon")
plot(re)
```

## Contribution

Contributions to this package are welcome - let us know if you need other distance measures or transformations, have any suggestions, or spotted a bug. 
The preferred method of contribution is through a GitHub pull request. 
Feel also free to contact us by creating [an issue](https://github.com/nowosad/spquery/issues).

